### 2021-02-25 text/draft.tex
implement metrics
spread of keywords

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data (\(N\) = 68'345) per department. Data field
\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
2'314.533, \(p < 0.001\). The data foundation is available at
\texttt{/edoc/analysis} and the chi-square statistic can be calculated
by calling \texttt{\_Analysis.chi\_square\_fit}.}
\end{figure}

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (X of all
keywords with Y of all occurrences). In both cases, the problem is due
to the fact that Wikidata's mapping of MeSH respectively YSO is only
partial. There can be two reasons for this state of affairs for a given
entry: either there is no match between Wikidata and YSO or MeSH (after
all, Wikidata is much larger than MeSH and YSO taken together), or there
is a match but it has not yet been added to the mapping. In the latter
case, at least with respect to YSO, there is a solution: Finto provides
a REST-sytle API to access the YSO vocabulary directly (see
https://api.finto.fi/). For each keyword in in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{\_Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json}

@@

@@

@@

\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{False negative} + \text{False positive}}\)

@@

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

>>>>

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data (\(N\) = 68'345) per department. Data field
\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
2'314.533, \(p < 0.001\). The data foundation is available at
\texttt{/edoc/analysis} and the chi-square statistic can be calculated
by calling
\texttt{\_Analysis.get\_\textasciitilde{}\textasciitilde{}\textasciitilde{}\textasciitilde{}chi\_square\_fit}.}
\end{figure}

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (26.9\% of
all keywords with 11\% of all occurrences). In both cases, the problem
is due to the fact that Wikidata's mapping of MeSH respectively YSO is
only partial. There can be two reasons for this state of affairs for a
given entry: either there is no match between Wikidata and YSO or MeSH
(after all, Wikidata is much larger than MeSH and YSO taken together),
or there is a match but it has not yet been added to the mapping. In the
latter case, at least with respect to YSO, there is a solution: Finto
provides a REST-sytle API to access the YSO vocabulary directly (see
https://api.finto.fi/). For each keyword in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{\_Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json}

@@

\hypertarget{discussion}{%
\paragraph{Discussion}\label{discussion}}

@@

!! How many author keywords per item? !! How many suggestions per item
are correct?

@@

\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}\)

@@

!! number of keywords per item; number of keywords with qid per item

!! how to deal with items that have more than 10 keywords in standard??

@@

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}
